The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}

### 2021-07-08 Addition.tex
Update Addition.tex

\subsection*{Participants}
The participants are students of the 5th grade and consist of two groups the control group [CG] and
the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
It should be ensured that both groups prior to the experiment perform academically similar, if not a
comparison post experiment will be difficult.
\newpage
\section{Results}
\begin{figure}[h]
    \includegraphics[width=\textwidth]{results.PNG}
\end{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{all.png}
\end{center}
\begin{figure}[h]
    \includegraphics[width=.5\textwidth]{female.png}
    \includegraphics[width=.5\textwidth]{male.png}
    \includegraphics[width=.5\textwidth]{fsav_msav.png}
    \includegraphics[width=.5\textwidth]{ferr_merr.png}
\end{figure}
\begin{figure}[h]
    \includegraphics[width=.5\textwidth]{fsav_merr.png}
    \includegraphics[width=.5\textwidth]{msav_ferr.png}
\end{figure}

\section{Discussion}
\section{Conclusion}
\section{References}
\end{document}

>>>>

\subsection*{Implementation}
We implemented a possible back-end, which can be used offline. You can find it 
at \url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}.
\subsection*{Participants}
The participants are students of the 5th grade and consist of two groups the control group [CG] and
the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
It should be ensured that both groups prior to the experiment perform academically similar, if not a
comparison post experiment will be difficult.
\newpage
\section{Results}
\begin{figure}[h]
    \includegraphics[width=\textwidth]{results.PNG}
\end{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{all.png}
\end{center}
\begin{figure}[h]
    \includegraphics[width=.5\textwidth]{female.png}
    \includegraphics[width=.5\textwidth]{male.png}
    \includegraphics[width=.5\textwidth]{fsav_msav.png}
    \includegraphics[width=.5\textwidth]{ferr_merr.png}\\\\\\\\
\end{figure}
\begin{figure}[h]
    \includegraphics[width=.5\textwidth]{fsav_merr.png}
    \includegraphics[width=.5\textwidth]{msav_ferr.png}
    \caption{These are the box-plots where we compared the different outcomes with each other. There were 100 reachable points.}
\end{figure}
We also calculated the t- and p-values to see which two groups have the most significant differences. We saw the biggest difference between the females from the control group and error group, where we got a t-value of 0.949 and a p-value of 0.345. This makes the relationship between error and non-error groups not significant enough, because their p-value is larger than 0.05.

\section{Discussion}
\section{Conclusion}
\section{References}
\url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}
\end{document}
